\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-15 paper/mswp2012-proposal.tex
Introduction - now in English ;)

More and more people are getting obese. They live unhealthy and do to less sport. Many health-reports in Europe and America describe the problem and show how fast the people are getting fat. Particular bad are the children, which also gets unhealthy. And these children are going to become serious problems when they are grown up. \\

Studies \citep{rki:2012} show, that about 23 Percent of the people in Germany are obese nowadays. These people don’t only look bad. They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.  \\

In near future this will cause a lot of financial claim in our health-care-system. More and more people have to get treated in a hospital because of health problems caused by being obese over the years.  \\

The only way we can reduce this costs in future, is to live nowadays healthier. And for this the software system should help. If people can get an bonus for living healthier, they will get motivated to do so. They will use the system in their live and reduce the risks to get one of the illnesses caused by obese.  \\

Every single person has a benefit when he uses the system. So he can live longer and healthier. We can say: \\
Mens sana in corpore sano \\
This Latin slogan means: In a healthier body is a healthier soul. People will feel happier, if they live healthier.  \\

Unfortunately it is not easy to motivate people to look on their own bodies. Many people are lazy and lay on the couch instead of going out for a walk. They buy junk food instead of fruits. Because they know how junk food tastes better. With this software system, the people should learn and accept a healthier way of living. They get a little benefit, when they buy an healthier fruit instead of junk food.  \\

These small benefits are combined in a challenge with all the other users of the system. So the motivation gets to a competition with a lot of other people living in a particular similar situation.  \\

Over all the health-care-system will lower the costs and so they can combine this system with their insurance-system. So people would have to use it for getting a cheaper insurance. So somebody who wants to live healthier can have a cheaper insurance.  \\

This project is accompanied by a scientific study. This study have to monitor the evolution of the health of the people while the use the system. This study show how efficient the system works. The iterative development of the system uses the data from the study for improving the output and to get healthier people.  \\

So everyone has a benefit with this system. The people are living healthier, happier and longer.  \\
% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

@@

 \begin{description}
  \item[MSWP] Management von Software Projekten
  \item[WP] Work Package
  \item[OECD] Organisation for Economic Co-operation and Development
  \item[RKI] Robert Koch Institut
 \end{description}

>>>>

Recent studies show that more and more people are getting obese these days due to an unhealthy lifestyle and way too less exercisement, especially in the so called western society. Many studies and health reports in Europe and America describe the problem and show an increasing trend towards being overweight. The biggest problem being the situation getting worse and worse - especially children are rapidly becoming a big part of the problem, the risk of being overweight is about 30 percent\footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. \\

Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays. Being overweight not only affects your attractiveness, it can lead to very serious health problems like hypertension, asthma, diabetes and other cardiovascular problems.  \\

In the Forbes List for the fattest nation, Austria ranks on place 52 with a fat rate of 57.1\%.\footnote{\url{http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}. Figure \ref{fig:obese_in_eu_pdf} shows a rather recent statistic of the situation in 25 European countries, divided by sex.

\begin{figure}[tb]
	\centering
	\includegraphics[width=1\textwidth]{images/introduction/1.jpg}
	\caption{Obese in the EU}
	\label{fig:obese_in_eu_pdf}
\end{figure}

One reason for the negative trend of childhood overweight are bad role models. Parents living an unhealthy lifestyle affect and influence their children. A recent study suggests that at-risk children are identifyable in their first years of life and tries to identify various risk factors \footnote{\url{http://news.stanford.edu/news/2004/july21/med-obesity-721.html}}. With increased age it gets harder to get in shape, the goal should be to teach children at young ages how to become and stay fit. In the future this negative trend will lead to an increased financial claim in our health care system - more and more people need expensive health treatments because of diseases caused by being obese over the years.  \\

The only way to stop this trend and to reduce the costs for health treatment is to live healthier today. This is the point where our modern health care system comes into play: We want to help people improving their lifestyle and staying fit by motivating them through the help of gamification and technology. Rankings against friends and neighbours as well as bonuses for reaching milestones are a vital part of our system. People shouldn't get forced to live healthy, they should do it self-motivated. We want to increase this motivation. This will eventually lead to a healthier society over time.  \\

Our goal is to make people realize how they can benefit from a healthier lifestyle. A latin quote goes as follows:

\begin{center}
	\emph{"Mens sana in corpore sano"}
\end{center}

A sound mind in a healthy body, people that are healthy feel happier. Unfortunately it is way harder to motivate people to look after themselves than it should be. One's weaker self is often blamed for becoming a so called modern couch potato. Combined with the increasing stress of today's achievement-oriented society this leads to long working hours without time for healthy meals or exercises. Most people ignore the fact that often small changes of their habits can lead to a healthier lifestyle without having to invest hours a day for doing sports. Taking the stairs instead of the elevator, using a standing desk instead of sitting in front of the computer all day long, taking the bike to work, buying fruits and healthy meals instead of chunkfood - all these things can dramatically improve your fitness and can be easily integrated as your day-to-day routines. What's missing? The motivation to do so. People are easy to influence (in a good sense). People are driven by results they can see and by competing with people they know. People want to be better than others, naturally. People enjoy being rewarded for their efforts. We want to use these inner forces and turn them into something good, we want to use them to help people improve their lifes. \\

Overall our modern health care system should lead to lowered costs for health care in general and it might be possible to integrate the system with private insurance systems. People would see another benefit of living healthy: cheaper insurance. People like to save money. \\

This project is accompanied by a scientific study. The goal of the study is to generate relevant data on which arrangements can motivate people the most and lead to best results as well as how people interact with a modern, technology-driven health care system, and how to improve these interactions. This data should lead to a good basis for future work on the topic. \\
% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

@@

 \begin{description}
  \item[MSWP] Management von Software Projekten
  \item[WP] Work Package
 \end{description}
